---
title: "SVAP_LabQue"
author: "Lavanya"
date: "September 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyr)
library(dplyr)
library(ggplot2)
```

## Analysing Datewise Onion Prices 

## Scraping year 2017 Datewise data till Sep19th 
```{r}

getwd()
Dailydata = read_html("../DailyWiseMarketArrivals.html") %>%
  html_node("#dnn_ctr966_DailyWiseMarketArrivals_GridView1") %>%
  html_table()

str(Dailydata)
View(Dailydata)

```

## Question 1
## Finding the State with highest Quantity Sales

## Refining the data
```{r}
#Changing the column names 
New_Cols = c('Date', 'Market', 'Quantity', 'Pricemin', 'Pricemax', 'ModPrice')
colnames(Dailydata) = New_Cols

#Converting all Price columns to numeric and Datatype of Date from Char to Date

Dailydata$Pricemax = as.numeric(Dailydata$Pricemax)
Dailydata$Pricemin = as.numeric(Dailydata$Pricemin)
Dailydata$ModPrice = as.numeric(Dailydata$ModPrice)
Dailydata$Date = as.Date(Dailydata$Date,"%d/%b/%Y")
head(Dailydata)

# Removing the Total row

Dailydata = Dailydata %>% filter(Quantity< 10000000)
tail(Dailydata)  
```
## Treating missing values - replacing the quantities with respective means
## Finding the columns with missing values, replace 0s with NAs

```{r}

#Calculate mean to replace missing values
Pricemin_mean = round(mean(Dailydata$Pricemin))
Pricemax_mean = round(mean(Dailydata$Pricemax))
ModPrice_mean = round(mean(Dailydata$ModPrice))

Pricemin_mean
Pricemax_mean
ModPrice_mean


#Replacing zeroes with NA
is.na(Dailydata$Pricemin) = !Dailydata$Pricemin
is.na(Dailydata$Pricemax) = !Dailydata$Pricemax
is.na(Dailydata$ModPrice) = !Dailydata$ModPrice

#Replacing missing values with mean

Dailydata = Dailydata %>% replace_na(list(Pricemin = Pricemin_mean,Pricemax = Pricemax_mean, ModPrice = ModPrice_mean))

View(Dailydata)
```

## Grouping by States

```{r}

Dailydata = Dailydata %>% 
  mutate(Market1 = Market) %>%
      separate(Market1,c("city","state","subdat"), sep="\\(")
head(Dailydata)

#Finding Total states under observation
Data_State = Dailydata %>% distinct(state)
Data_State
str(Dailydata)

```

## Cleaning Data
## Replacing the NA in State column for few major cities and removing Duplicate State names, and adding state as DELHI for City Delhi

```{r}

Clean_Data = Dailydata %>% 
  mutate(state = replace(state,
                            is.na(state) & city == 'BANGALORE',
                          'KNT)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'CHENNAI', 
                          'TN)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'BULANDSHAHR', 
                          'UP)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'LUCKNOW', 
                          'UP)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'SHAHJAHANPUR',
                          'UP)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'MUMBAI', 
                          'MS)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'NAGPUR', 
                          'MS)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'JAIPUR', 
                          'RJ)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'KOLKATA', 
                          'WB)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'HYDERABAD', 
                          'TELANGANA)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'GUWAHATI', 
                          'AS)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'BHOPAL', 
                          'MP)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'SHIMLA', 
                          'HP)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'TRIVANDRUM', 
                          'KER)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'CHANDIGARH', 
                          'CHGARH)')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'JAMMU', 
                          'JK')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'DELHI', 
                          'DELHI')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'GANGTOK',
                          'SIKKIM')) %>%
  mutate(state = replace(state,
                            is.na(state) & city == 'PATNA',
                          'BIHAR')) %>%
  mutate(state = replace(state,
                            state == 'Telangana)' | state == 'TELANGANA)',
                          'TELANGANA')) %>%
  mutate(state = replace(state,
                            state == 'F&V) ' & city == 'SHIVPURI', 
                          'MP)')) %>%
  mutate(state = replace(state,
                            state == 'RAJ)' | state == 'RJ)',
                          'RAJ)')) %>%
  mutate(state = replace(state,
                            state == 'TN)' | state == 'TN) ',
                          'TN)'))
         
View(Clean_Data)
str(Clean_Data)

```


## Finding Distinct states 
```{r}
Data_State_new = Clean_Data %>% distinct(state)
Data_State_new

```

## Calculating Quantitysales based on states

```{r}
Sta_qty = Clean_Data %>% group_by(state) %>% 
  summarise(Quant_Sales = sum(Quantity)) %>% 
  arrange(desc(Quant_Sales)) 
head(Sta_qty)


```

## INSIGHT
## Therefore the state with highest Quantity sales is 'MAHARASHTRA'
## PLotting the Graph


```{r}

library(plotly)
State_Quant_plot = ggplot(Sta_qty)+ aes(state,Quant_Sales, fill = state) + geom_col(width=1)
ggplotly(State_Quant_plot)

```

## Hence the state with highest Quantity sales is MS- Maharashtra, So Lets use Linear regression model and predict the Quantity sales for next 30 days


## Question2
## Predict the daily price for the next 30 days for state with highest Quantity Sales.

```{r}

# Filtering Maharashtra State Data and calculate mean of Moderate price per day 
# and select Date and Moderate price
MH_Data = Clean_Data %>% filter(state==c("MS)")) %>% group_by(Date) %>%
  summarise(ModPrice_new = mean(ModPrice)) %>% 
  select(Date,ModPrice_new)
 
#renaming column names as ds and y 
colnames(MH_Data) = c('ds' ,'y')

#Forecasting using prophet forecaster for the month of october
library(prophet)
m = prophet(MH_Data)
Predicted_DailyPrice = make_future_dataframe(m, period=45, freq="d")
forecast= predict(m,Predicted_DailyPrice)

plot(m,forecast)
tail(Predicted_DailyPrice)
View(MH_Data)

```

## From the above plot we can find that the Onion prices is likely to increase in the month of October and beginning of November.